Datasets used in thesis

### 2015-04-24 Rmarkdown/datasets.Rmd
Changes suggested by Belinda.

1. Genetic variants were called using the `bissnp_easy_usage.pl` script included with `Bis-SNP (v0.82.2)`.
2. M-bias was estimated using `bismark_methylation_extractor` with the `--mbias_only` flag set. These output files were then analysed using the  `MethylationTuples` R package (see section \ref{sec:MethylationTuples}) and all read-positions with an CpG normalised read-position methylation level more than $0.03$ from the median, i.e., $|nrplml_{CpG} - median(rplm_{CpG})| > 0.03$, were excluded from methylation calling (read 1 and read 2 analysed separately where applicable).
3. CpG methylation calling was performed using `methtuple (v1.4.0)` for m-tuples $\text{m} = 1, \ldots, 8$. CpG 2-tuples were called both with and without the `--all-combinations` flag; all other tuple sizes were called without the `--all-combinations` flag.
4. Sample-level m-tuples were combined at the dataset-level using the `MethylationTuples` R package (see \ref{sec:MethylationTuples}). Specifically, a `MethPat` object was created for each of the EPISCOPE, Lister, Seisenberger and Ziller datasets for 1-tuples, 2-tuples, 2ac-tuples (2-tuples with `--all-combinations`), 3-tuples and 4-tuples. I did not create `MethPat` objects for m-tuples with $\text{m} > 4$ because the data are too sparse at this larger sizes to be generally useful.

>>>>

1. Genetic variants were called using the `bissnp_easy_usage.pl` script included with `Bis-SNP (v0.82.2)`.
2. M-bias was estimated using `bismark_methylation_extractor` with the `--mbias_only` flag set. These output files were then analysed using the  `MethylationTuples` R package (see section \ref{sec:MethylationTuples}) and all read-positions with an CpG normalised read-position methylation level ($nrpml$) more than $0.03$ from the median, i.e., $|nrpml_{CpG} - median(nrpml_{CpG})| > 0.03$, were excluded from methylation calling (read 1 and read 2 analysed separately where applicable).
3. CpG methylation calling was performed using `methtuple (v1.4.0)` for m-tuples $\text{m} = 1, \ldots, 8$. CpG 2-tuples were called both with and without the `--all-combinations` flag; all other tuple sizes were called without the `--all-combinations` flag.
4. Sample-level m-tuples were combined at the dataset-level using the `MethylationTuples` R package (see \ref{sec:MethylationTuples}). Specifically, a `MethPat` object was created for each of the EPISCOPE, Lister, Seisenberger and Ziller datasets for 1-tuples, 2-tuples, 2ac-tuples (2-tuples with `--all-combinations`), 3-tuples and 4-tuples. I did not create `MethPat` objects for m-tuples with $\text{m} > 4$ because the data are too sparse at this larger sizes to be generally useful.
